### 2020-04-04 Paper_EV/Paper_EV.tex
Backup update 04_04

\textbf{Latin Letters}
% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
    \textbf{Symbol} & \textbf{Unit} & \textbf{Description} \\ [1.2ex] 
    $A(s),~A(z)$ & -- & Transfer function of the actuator dynamics \\ 
    $A'(s),~A'(z)$ & -- & Transfer function of the actuator dynamics model \\
    $a(t)$ & -- & Function of the first order lag element in time domain \\
    $b$ & $m$ & Lever arm of the rotors to the C.G. along the body $y$-axis \\
    $d$ & $m/s^2$ & Disturbance \\
    $d_0, d_1, d_2$ & -- & Denominator coefficients of the discrete second order filter \\
    $E(t)$ & -- & Objective function \\
    $\bm{F}$ & $N$ & Force vector \\
    $\bm{F}_A$ & $N$ & Aerodynamic force vector \\
    $\bm{F}_G$ & $N$ & Gravitational force vector \\
    $\bm{F}_P$ & $N$ & Propulsive force vector \\
    $\bm{f}(\bm{x})$ & -- & Nonlinear vector field \\
    $\bm{G}$ & -- & Control effectiveness matrix of the outer loop \\
    $\bm{G}_1$ & -- & Control effectiveness matrix of the inner loop \\
    $\bm{G}_2$ & -- & Control effectiveness matrix of the inner loop \\
    $\bm{G}_{inner}$ & -- & Dynamics matrix of the inner loop \\
    $\bm{G}_{outer}$ & -- & Dynamics matrix of the outer loop \\
    $\bm{G}(x)$ & -- & Input matrix \\
    $g$ & $m/s^2$ & Gravitational acceleration \\
    $H(s),~H(z)$ & -- & Transfer function of the second order filter \\
    $\bm{h}(\bm{x})$ & -- & Nonlinear vector field \\
    $\bm{I}$ & $Nm^2$ & Inertia tensor of the quadrotor \\
    $\bm{I_{rzz}}$ & $Nm^2$ & $zz$-element of the inertia tensor of the rotor \\
    $i$ & -- & Relative degree of the dynamic system \\
    $K$ & -- & Compensation gain \\
    $K_{cmd}$ & -- & Thrust mapping parameter \\
    $k$ & $kg/s$ & Drag coefficient \\ %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  %\captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_latin_1}
\end{table}

@@

% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
    $k$ & -- & Gain of the actuator dynamics \\ 
    $k_F$ & $\frac{N}{rad/s}$ & Force constant of the rotors \\
    $k_M$ & $\frac{Nm}{rad/s}$ & Moment constant of the rotors \\
    $L$ & -- & Lie derivative operator \\
    $l$ & $m$ & Lever arm of the rotors to the C.G. along the body $y$-axis \\
    $\bm{M}$ & $Nm$ & Moment vector \\
    $\bm{M}_A$ & $Nm$ & Aerodynamic Moment vector \\
    $\bm{M}_c$ & $Nm$ & Control moment vector \\
    $\bm{M}_G$ & $Nm$ & Gravitational Moment vector \\
    $\bm{M}_{gyro}$ & $Nm$ & Moment vector due to the gyroscopic effects of the rotor \\
    $\bm{M}_{OB}$ & -- & Transformation matrix from the body-fixed into NED frame \\
    $\bm{M}_P$ & $Nm$ & Propulsion moment vector \\
    $m$ & $kg$ & Mass of the quadrotor \\
    $m_{cf}$ & $kg$ & Mass of the Crazyflie quadrotor \\
    $m_r$ & $kg$ & Additional mass (disturbance \\
    $n$ & -- & Number of samples \\
    $n_0, n_1, n_2$ & -- & Numerator coefficients of the discrete second order filter \\
    $P$ & -- & Parameter \\
    $p$ & $rad/s$ & Roll rate \\ 
	$q$ & $rad/s$ & Pitch rate \\
    $r$ & $rad/s$ & Yaw rate \\
	$s$ & -- & Laplace variable \\
    $T$ & $N$ & Thrust \\
	$T$ & $s$ & Time constant of the actuator dynamics \\
    $T_{cmd}$ & -- & Thrust in motor units \\
	$T_s$ & $s$ & Sample time of the controller \\
    $\tilde{T}$ & $N$ & Thrust increment\\
	$t$ & $s$ & Time \\    
    $u$ & -- & Input vector \\
    $\bm{u}_c$ & -- & Control vector \\
    $u$ & $m/s$ & $x$-component of the velocity vector \\ %[0.5ex]
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_latin_2}
\end{table}

@@

% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
    $V$ & $m/s$ & Component of the velocity vector \\ 
    $v$ & $m/s$ & $y$-component of the velocity vector \\
    $ \bm{v}$ & $m/s$ & Velocity vector \\
    $W$ & $N$ & Weight of the quadrotor \\
    $w$ & $m/s$ & $z$-component of the velocity vector \\
    $\bm{x}$ & -- & State vector \\
    $x$ & $m$ & Position coordinate in $x$-direction \\
    $\bm{y}$ & -- & Output vector \\
    $y$ & $m$ & Position coordinate in $y$-direction \\
    $\bm{z} $ & -- & Transformed state vector \\
    $z$ & -- & z-Transformation variable \\
    $z$ & $m$ & Position coordinate in $z$-direction \\ %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_latin_3}
\end{table}

@@

\textbf{Greek Letters}
% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
    \textbf{Symbol} & \textbf{Unit} & \textbf{Description} \\ [1.2ex] 
    $\alpha$ & -- & Parameter of the discrete first order lag element \\ 
    $\zeta$ & -- & Relative damping coefficient of the second order filter \\
    $\bm{\eta}$ & $rad$ & Attitude vector \\
    $\Theta$ & $rad$ & Pitch angle \\
    $\tilde{\Theta}$ & $rad$ & Pitch angle increment \\
    $\Theta_c$ & $rad$ & Control pitch angle \\
    $\bm{\nu}$ & -- & Virtual control input vector \\
    $\bm{\nu}_{\bm{\dot{v}}}$ & $m/s^2$ & Virtual control input vector of the outer loop \\
    $\bm{\nu}_{\bm{\dot{\omega}}}$ & $rad/s^2$ & Virtual control input vector of the inner loop \\
    $\bm{\xi}$ & $m$ & Position vector \\
    $\Phi$ & $rad$ & Roll/Bank angle \\
    $\tilde{\Phi}$ & $rad$ & Roll angle increment \\
    $\Phi_c$ & $rad$ & Control roll angle \\
	$\bm{\phi}(\bm{x})$ & -- & State transformation function \\ %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_greek}
\end{table}

\textbf{Indices}
% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{10cm}} 
    \textbf{Symbol} & \textbf{Description} \\ [1.2ex] 
    $0$ & Initial point in time \\ 
    $a$ & Passed through the actuator dynamics \\ 
    $B$ & Body-fixed coordinate frame \\ 
    $D$ & Down \\
    $E$ & East \\ 
    $f$ & Filtered \\ 
    $G$ & Center of gravity \\ 
    $G$ & Gravitational \\
    $K$ & Kinematic coordinate frame \\
    $N$ & North \\
    $O$ & North-East-Down coordinate frame \\
    $R$ & Reference point \\
    $x$ & $x$-component of a variable \\
	$y$ & $y$-component of a variable \\
	$z$ & $z$-component of a variable \\ %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_indices}
\end{table}

>>>>

\textbf{Latin Letters}
% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
    \textbf{Symbol} & \textbf{Unit} & \textbf{Description} \\ [1.2ex] 
    $A(s),~A(z)$ & -- & Transfer function of the actuator dynamics \\ 
    $A'(s),~A'(z)$ & -- & Transfer function of the actuator dynamics model \\
    $a(t)$ & -- & Function of the first order lag element in time domain \\
    $b$ & $m$ & Lever arm of the rotors to the C.G. along the body $y$-axis \\
    $d$ & $m/s^2$ & Disturbance \\
    $d_0, d_1, d_2$ & -- & Denominator coefficients of the discrete second order filter \\
    $E(t)$ & -- & Objective function \\
    $\bm{F}$ & $N$ & Force vector \\
    $\bm{F}_A$ & $N$ & Aerodynamic force vector \\
    $\bm{F}_G$ & $N$ & Gravitational force vector \\
    $\bm{F}_P$ & $N$ & Propulsive force vector \\
    $\bm{f}(\bm{x})$ & -- & Nonlinear vector field \\
    $\bm{G}$ & -- & Control effectiveness matrix of the outer loop \\
    $\bm{G}_1$ & -- & Control effectiveness matrix of the inner loop \\
    $\bm{G}_2$ & -- & Control effectiveness matrix of the inner loop \\
    $\bm{G}_{inner}$ & -- & Dynamics matrix of the inner loop \\
    $\bm{G}_{outer}$ & -- & Dynamics matrix of the outer loop \\
    $\bm{G}(x)$ & -- & Input matrix \\
    $g$ & $m/s^2$ & Gravitational acceleration \\
    $H(s),~H(z)$ & -- & Transfer function of the second order filter \\
    $\bm{h}(\bm{x})$ & -- & Nonlinear vector field \\
    $\bm{I}$ & $Nm^2$ & Inertia tensor of the quadrotor \\
    $\bm{I_{rzz}}$ & $Nm^2$ & $zz$-element of the inertia tensor of the rotor \\
    $i$ & -- & Relative degree of the dynamic system \\
    $K$ & -- & Compensation gain \\
    $K_{cmd}$ & -- & Thrust mapping parameter \\
    $K_{\eta}$ & -- & Gain of the inner loop \\ %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  %\captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_latin_1}
\end{table}

@@

% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
    $K_{\omega}$ & -- & Gain of the inner loop \\
    $K_{\xi}$ & -- & Gain of the outer loop \\
    $K_{\dot{v}}$ & -- & Gain of the outer loop \\
    $k$ & $kg/s$ & Drag coefficient \\ 
    $k$ & -- & Gain of the actuator dynamics \\ 
    $k_F$ & $\frac{N}{rad/s}$ & Force constant of the rotors \\
    $k_M$ & $\frac{Nm}{rad/s}$ & Moment constant of the rotors \\
    $L$ & -- & Lie derivative operator \\
    $l$ & $m$ & Lever arm of the rotors to the C.G. along the body $y$-axis \\
    $\bm{M}$ & $Nm$ & Moment vector \\
    $\bm{M}_A$ & $Nm$ & Aerodynamic Moment vector \\
    $\bm{M}_c$ & $Nm$ & Control moment vector \\
    $\bm{M}_G$ & $Nm$ & Gravitational Moment vector \\
    $\bm{M}_{gyro}$ & $Nm$ & Moment vector due to the gyroscopic effects of the rotor \\
    $\bm{M}_{OB}$ & -- & Transformation matrix from the body-fixed into NED frame \\
    $\bm{M}_P$ & $Nm$ & Propulsion moment vector \\
    $m$ & $kg$ & Mass of the quadrotor \\
    $m_{cf}$ & $kg$ & Mass of the Crazyflie quadrotor \\
    $m_r$ & $kg$ & Additional mass (disturbance \\
    $n$ & -- & Number of samples \\
    $n_0, n_1, n_2$ & -- & Numerator coefficients of the discrete second order filter \\
    $P$ & -- & Parameter \\
    $p$ & $rad/s$ & Roll rate \\ 
	$q$ & $rad/s$ & Pitch rate \\
    $r$ & $rad/s$ & Yaw rate \\
	$s$ & -- & Laplace variable \\
    $T$ & $N$ & Thrust \\
	$T$ & $s$ & Time constant of the actuator dynamics \\
    $T_{cmd}$ & -- & Thrust in motor units \\
	$T_s$ & $s$ & Sample time of the controller \\
    $\tilde{T}$ & $N$ & Thrust increment \\ %[0.5ex]
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_latin_2}
\end{table}

@@

% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
	$t$ & $s$ & Time \\    
    $u$ & -- & Input vector \\
    $\bm{u}_c$ & -- & Control vector \\
    $u$ & $m/s$ & $x$-component of the velocity vector \\
    $V$ & $m/s$ & Component of the velocity vector \\ 
    $v$ & $m/s$ & $y$-component of the velocity vector \\
    $ \bm{v}$ & $m/s$ & Velocity vector \\
    $W$ & $N$ & Weight of the quadrotor \\
    $w$ & $m/s$ & $z$-component of the velocity vector \\
    $\bm{x}$ & -- & State vector \\
    $x$ & $m$ & Position coordinate in $x$-direction \\
    $\bm{y}$ & -- & Output vector \\
    $y$ & $m$ & Position coordinate in $y$-direction \\
    $\bm{z} $ & -- & Transformed state vector \\
    $z$ & -- & z-Transformation variable \\
    $z$ & $m$ & Position coordinate in $z$-direction %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_latin_3}
\end{table}

@@

\textbf{Greek Letters}
% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
    \textbf{Symbol} & \textbf{Unit} & \textbf{Description} \\ [1.2ex] 
    $\alpha$ & -- & Parameter of the discrete first order lag element \\ 
    $\zeta$ & -- & Relative damping coefficient of the second order filter \\
    $\bm{\eta}$ & $rad$ & Attitude vector \\
    $\Theta$ & $rad$ & Pitch angle \\
    $\tilde{\Theta}$ & $rad$ & Pitch angle increment \\
    $\Theta_c$ & $rad$ & Control pitch angle \\
    $\bm{\nu}$ & -- & Virtual control input vector \\
    $\bm{\nu}_{\bm{\dot{v}}}$ & $m/s^2$ & Virtual control input vector of the outer loop \\
    $\bm{\nu}_{\bm{\dot{\omega}}}$ & $rad/s^2$ & Virtual control input vector of the inner loop \\
    $\bm{\xi}$ & $m$ & Position vector \\
    $\Phi$ & $rad$ & Roll/Bank angle \\ %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_greek_1}
\end{table}

% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
    $\tilde{\Phi}$ & $rad$ & Roll angle increment \\
    $\Phi_c$ & $rad$ & Control roll angle \\
	$\bm{\phi}(\bm{x})$ & -- & State transformation function %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_greek_2}
\end{table}

\textbf{Indices}
% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{10cm}} 
    \textbf{Symbol} & \textbf{Description} \\ [1.2ex] 
    $0$ & Initial point in time \\ 
    $a$ & Passed through the actuator dynamics \\ 
    $B$ & Body-fixed coordinate frame \\ 
    $D$ & Down \\
    $E$ & East \\ 
    $f$ & Filtered \\ 
    $G$ & Center of gravity \\ 
    $G$ & Gravitational \\
    $K$ & Kinematic coordinate frame \\
    $N$ & North \\
    $O$ & North-East-Down coordinate frame \\
    $R$ & Reference point \\
    $x$ & $x$-component of a variable \\
	$y$ & $y$-component of a variable \\
	$z$ & $z$-component of a variable %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_indices}
\end{table}
